Figures

### 2017-01-14 figures/partnerSIR.tex
diagrams

\newcommand{\instswitchflowvec}{ 
	\draw[->, very thick] (SS) to (SI); 
	\draw[->, very thick] (SI) to (II); 
}

\newcommand{\instswitchnoepcinf}{
	\draw[->, blue, dashed, very thick] (SI)
		to [bend right=45] (SItoII);
	\draw[->, blue, dashed, very thick] (SI)
		to [bend left=45] (SStoSI);
}

\newcommand{\instswitchepcinf}{
	\draw[->, red, dashed, very thick] (II)
		to [bend right=45] (SItoII);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=70] (SStoSI);
}

@@

\newcommand{\instswitchboxes}{
	\node(SS)[bigcompartment]{SS};
	\node(SStoSI)[right=of SS]{};
	\node(SI)[bigcompartment, right=of SStoSI]{SI};
	\node(SItoII)[right=of SI]{};
	\node(II)[bigcompartment, right=of SItoII]{II};
}

>>>>

\newcommand{\instswitchflowvec}{ 
	\draw[->, very thick] (SI) to (II); 
}

\newcommand{\instswitchepcflowvec}{
	\draw[->, very thick] (SS) to (SI); 
}

\newcommand{\instswitchmixing}{
	\draw[<->, dotted, very thick] (SS) to (pool);
	\draw[<->, dotted, very thick] (SI) to (pool);
	\draw[<->, dotted, very thick] (II) to (pool);
}

\newcommand{\instswitchnoepcinf}{
	\draw[->, blue, dashed, very thick] (SI)
		to [bend right=45] (SItoII);
}

\newcommand{\instswitchepcinf}{
	\draw[->, red, dashed, very thick] (SI)
		to [bend left=45] (SStoSI);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=45] (SItoII);
	\draw[->, red, dashed, very thick] (II)
		to [bend left=70] (SStoSI);
}

@@

\newcommand{\instswitchboxes}{
	\node(SS)[bigcompartment]{SS};
	\node(SStoSI)[right=of SS]{};
	\node(SI)[bigcompartment, right=of SStoSI]{SI};
	\node(SItoII)[right=of SI]{};
	\node(II)[bigcompartment, right=of SItoII]{II};
	\node(pool)[compartment, very thick, above = 10mm of SI, text width = 40mm, align = center, draw = black, top color = white, bottom color = white, dotted]{temporary mixing pool};
}
